Proof equivalence in MLL is PSPACE-complete

### 2015-01-30 main/LMCS.tex
Correct references

\begin{remark}
A main distinction with the proof nets of \cite{Blute-Cockett-Seely-Trimble-1994} is that the latter are defined as graphs whose vertices represent inferences, and whose edges represent formulae. This formulation allows an easy inclusion of cuts, which are not present in our proof nets. That the jumps from $\bot$-vertices in these graphs are attached to edges, not vertices, is a natural choice given the categorical view of $\bot$-introduction as the isomorphism $A\to A\pr\bot$.
\end{remark}

@@

\begin{proposition}[\cite{Blute-Cockett-Seely-Trimble-1994,Hughes-2012-nets}]
\label{prop:proof nets work}
%
If $\Pi\toNet\links$ and $\Pi'\toNet\links'$, then $\Pi\perm\Pi'$ if and only if $\links\perm\links'$.
%
\end{proposition}

@@

Figure~\ref{fig:_*_,1,1,1,_*_} uses the diagrammatic notation to display the rewiring relation over the proof nets for the sequent $\bot\tn\bot,1,1,1,\bot\tn\bot$, an interesting example also highlighted in \cite{Lamarche-Strassburger-2005}. There are 24 proof nets in total, forming two equivalence classes, each consisting of a single cyclic rewiring path.

>>>>

\begin{remark}
A main distinction with the proof nets of \cite{Blute-Cockett-Seely-Trimble-1996} is that the latter are defined as graphs whose vertices represent inferences, and whose edges represent formulae. This formulation allows an easy inclusion of cuts, which are not present in our proof nets. That the jumps from $\bot$-vertices in these graphs are attached to edges, not vertices, is a natural choice given the categorical view of $\bot$-introduction as the isomorphism $A\to A\pr\bot$.
\end{remark}

@@

\begin{proposition}[\cite{Blute-Cockett-Seely-Trimble-1996,Hughes-2012-nets}]
\label{prop:proof nets work}
%
If $\Pi\toNet\links$ and $\Pi'\toNet\links'$, then $\Pi\perm\Pi'$ if and only if $\links\perm\links'$.
%
\end{proposition}

@@

Figure~\ref{fig:_*_,1,1,1,_*_} uses the diagrammatic notation to display the rewiring relation over the proof nets for the sequent $\bot\tn\bot,1,1,1,\bot\tn\bot$, an interesting example also highlighted in \cite{Strassburger-Lamarche-2004}. There are 24 proof nets in total, forming two equivalence classes, each consisting of a single cyclic rewiring path.
